### 2014-11-09 heat-transfer.tex
Update ht plot.

To further improve locality, we split the second rule to
not send small $\delta$ values if the target node is in another
thread (Fig.~\ref{code:ht_better}). The \textbf{Local-Only} line in
Fig.~\ref{results:ht} shows that improving locality by disabling small updates
improves the execution time of HT. XXX update figure

>>>>

To further improve locality, we split the second rule to
not send small $\delta$ values if the target node is in another
thread (Fig.~\ref{code:ht_better}). The \textbf{Local-Only/Coordinated} line in
Fig.~\ref{results:ht} shows that this new version performs better due to
improved locality, exhibiting linear scalability over the regular version.
However, this come at the price of increased errors in the computed heat values.
